Visual narratives of the Covid-19 pandemic

### 2022-01-04 JDSSV_editorialprocess.Rmd

---
documentclass: jdssv
author:
  - name: Susan Vanderplas
    affiliation: University of Nebraska–Lincoln
    address: |
      | Department of Statistics
      | University of Nebraska–Lincoln
      | 349A Hardin Hall 
      | Lincoln, NE 68583-0963, USA
    email: \email{susan.vanderplas@unl.edu}
    url: https://statistics.unl.edu/susan-vanderplas
  - name: Adalbert F. X. Wilhelm
    affiliation: Jacobs University Bremen
    # To add another line, use \AND at the end of the previous one as above
    address: |
      |  Department of Psychology and Methods
      |  Jacobs University Bremen gGmbH
      |  Campus Ring 1
      |  28759 Bremen
    email: \email{a.wilhelm@jacobs-university.de}
    url: http://www.jacobs-university.de/directory/wilhelm
    # use a different affiliation in adress field (differently formated here)
    # affiliation2: Universitat Autònoma de Barcelona
title:
  formatted: "Visual narratives of the Covid-19 pandemic"
  # If you use tex in the formatted title, also supply version without
  plain:     "Visual narratives of the Covid-19 pandemic"
  # For running headers, if needed
  short:     "Visual narratives of Covid-19"
abstract: >
    Covid-19 has created a world-wide interest in understanding the dynamics of a pandemic. Hence, numerous media outlets as well as researchers have produced comprehensive data visualizations to illustrate the relevant trends and figures. In this paper, we will look at an elective choice of Covid-19 data visualizations to evaluate and discuss currently established visualization tools in their capacity to provide a communication channel both within the data science team and also between data analyst, domain experts and a more general interested audience. While there is no fixed catalogue of evaluation criteria for data visualizations we will try to provide an overview on the different core aspects of visualization evaluation and their competing principles.
keywords:
  # exploratory data visualisation
  formatted: [JDSSV, style guidelines, comma-separated, not capitalized, "\\proglang{R}"]
  plain:     [JDSSV, style guidelines, comma-separated, not capitalized, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{longtable}
  \usepackage{booktabs}
  \newcommand{\class}[1]{`\code{#1}'}
  \newcommand{\fct}[1]{\code{#1()}}
  \newcommand{\ma}[1]{\ensuremath{\mathbf{#1}}}
output: rticles::jss_article
---

>>>>

---
documentclass: jdssv
author:
  - name: Patrick J.F. Groenen
    affiliation: Erasmus University Rotterdam
    # use this syntax to add text on several lines
    address: |
      | Econometric Institute
      | Erasmus School of Economics
      | Erasmus University Rotterdam
      | P.O. Box  1738 
      | 3000 DR Rotterdam, The Netherlands
    email: \email{groenen@ese.eur.nl}
    url: https://personal.eur.nl/groenen/
  - name: Stefan Van Aelst
    affiliation: KU Leuven
    # To add another line, use \AND at the end of the previous one as above
    address: |
      |  Department of Mathematics
      |  KU Leuven
      |  Celestijnenlaan 200B
      |  3001 Leuven, Belgium
    email: \email{Stefan.VanAelst@kuleuven.be}
    url: https://wis.kuleuven.be/statdatascience/robust
    # use a different affiliation in adress field (differently formated here)
    # affiliation2: Universitat Autònoma de Barcelona
title:
  formatted: "Guidelines for the Journal of Data Science, Statistics, and Visualisation"
  # If you use tex in the formatted title, also supply version without
  plain:     "Guidelines for the Journal of Data Science, Statistics, and Visualisation Version 0.3"
  # For running headers, if needed
  short:     "JDSSV Guidelines, Version 0.3"
abstract: >
    This short article illustrates how to write a manuscript for the   \emph{Journal of Data Science, Statistics and Visualisation} (JDSSV) using its \LaTeX\ style files.   Please follow JDSSV's style guidelines precisely. Also, it is recommended to keep the \LaTeX\ code as simple as possible, that is, avoid inclusion of packages/commands that are not necessary. 
keywords:
  # at least one keyword must be supplied
  formatted: [JDSSV, style guidelines, comma-separated, not capitalized, "\\proglang{R}"]
  plain:     [JDSSV, style guidelines, comma-separated, not capitalized, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{longtable}
  \usepackage{booktabs}
  \newcommand{\class}[1]{`\code{#1}'}
  \newcommand{\fct}[1]{\code{#1()}}
  \newcommand{\ma}[1]{\ensuremath{\mathbf{#1}}}
output: rticles::jss_article
---
